---
title: "ReproRes Poll Class 02"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    theme: yeti
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.width = 10,
  fig.height = 5
)

# [Poll](https://forms.gle/1EY8WcHKyXQvxqMz9)

library(flexdashboard)
library(kableExtra)
library(tidyverse)
library(googlesheets4)
options(gargle_oauth_email = "debruine@gmail.com")
library(ggthemes)
library(see)
library(ggwordcloud) # for word clouds
library(tidytext) # for manipulating text for word clouds
```

```{r, eval = TRUE}
theme_set(theme_fivethirtyeight(base_size = 24))
scale_fill <- scale_fill_brewer(palette = "Spectral", drop=FALSE)
scale_colour <- scale_colour_brewer(palette = "Spectral", drop=FALSE)
```

```{r}
# read data
url <- "1mZlGcQecowigXVUN_0HsnLPEpSaE0tXfoCfw6Lvv2vQ"
data <- read_sheet(url, sheet = "Week2") %>%
  filter(row_number() != 1)


engage <- c(book = "Read the book", 
            videos = "Watched the videos", 
            exercise = "Did the formative exercise",
            none = "I didn't get a chance this week")

n <- nrow(data)
```

`r n` Participants

Row {data-height=400}
-----------------------------------------------------------------------

### How did you engage with Chapter 1?

```{r}
subdat <- select(data, x = 2) %>%
  separate_rows(x, sep = ", ") %>%
  mutate(x = factor(x, rev(engage), rev(names(engage))))

ggplot(subdat, aes(x = x, fill = x)) +
  geom_bar(show.legend = FALSE, colour = "black") +
  scale_x_discrete(name = "",  drop=FALSE) +
  scale_y_continuous(name = "", breaks = 0:11*5) +
  scale_fill +
  coord_flip(ylim = c(0, n)) 
```

### How did you engage with Chapter 2?

```{r}
subdat <- select(data, x = 3) %>%
  separate_rows(x, sep = ", ") %>%
  mutate(x = factor(x, rev(engage), rev(names(engage))))

ggplot(subdat, aes(x = x, fill = x)) +
  geom_bar(show.legend = FALSE,colour = "black") +
  scale_x_discrete(name = "",  drop=FALSE) +
  scale_y_continuous(name = "", breaks = 0:11*5) +
  scale_fill +
  coord_flip(ylim = c(0, n)) 
```


Row {data-height=400}
-----------------------------------------------------------------------

### What parts of Skills Self-Assessment did you find challenging or impossible?

```{r}
ssa_levels <- c("combine data" = "Combining the data from two files", 
                "subject descriptives" = "Calculating the participant descriptives", 
                "trial exclusion" = "Determining how many trials were excluded", 
                "trial descriptives" = "Calculating the trial descriptives", 
                "analysis" = "Running the analyses",
                "none" = "none")

subdat <- select(data, x = 5) %>%
  separate_rows(x, sep = ", ") %>%
  mutate(x = ifelse(is.na(x), "none", x)) %>%
  mutate(x = factor(x, rev(ssa_levels), rev(names(ssa_levels))))

ggplot(subdat, aes(x = x, fill = x)) +
  geom_bar(show.legend = FALSE) +
  scale_x_discrete(name = "",  drop=FALSE) +
  scale_y_continuous(name = "", breaks = 0:11*5) +
  scale_fill +
  coord_flip(ylim = c(0, n)) 
```



### How did you engage with the Skills Self-Assessment?

```{r}
skass <- select(data, skass = 4) %>%
  count(skass) %>%
  mutate(skass = glue::glue("({round(100*n/sum(n))}%) {skass}"))

treemap::treemap(skass,
  index="skass",
  vSize="n",
  title = "",
  palette = "Spectral",
  inflate.labels = TRUE
)
```

Row {data-height=400}
-----------------------------------------------------------------------

### How are you accessing RStudio?

```{r}
subdat <- select(data, x = 9) %>%
  separate_rows(x, sep = ", ") %>%
  filter(!is.na(x))

ggplot(subdat, aes(x = x, fill = x)) +
  geom_bar(show.legend = FALSE, color = "black") +
  scale_x_discrete(name = "",  drop=FALSE) +
  scale_y_continuous(name = "", breaks = 0:11*5) +
  scale_fill +
  coord_flip(ylim = c(0, n)) 
```


### Have you been studying in a group?

```{r}
subdat <- select(data, x = 6) %>%
  mutate(x = factor(x, rev(c("Yes", "No, but I'd like to", "No, and I'd rather not"))))

ggplot(subdat, aes(x = x, fill = x)) +
  geom_bar(show.legend = FALSE, colour = "black") +
  scale_x_discrete(name = "",  drop=FALSE) +
  scale_y_continuous(name = "", breaks = 0:11*5) +
  scale_fill +
  coord_flip(ylim = c(0, n)) 
```

Row {data-height=400}
-----------------------------------------------------------------------

### List concepts you learned in Chapters 1 and 2 that you feel confident about.

```{r}
omitted <- c(stop_words$word, "im", 0:9)

words <- select(data, confident = 7) %>%
  filter(!is.na(confident)) %>%
  unnest_tokens(output = "word", input = "confident") %>%
  count(word) %>%
  filter(!word %in% omitted) %>%
  slice_max(order_by = n, n = 25, with_ties = FALSE)

ggplot(words, aes(label = word, colour = word, size = n)) +
  geom_text_wordcloud_area() +
  scale_size_area(max_size = 14) +
  theme_minimal(base_size = 10) +
  scale_color_see_d(palette = "ice") 
```



### List concepts you learned in Chapters 1 and 2 that you feel less confident about and would like reviewed in class today.

```{r}
omitted <- c(stop_words$word, "im", 0:9)

words <- select(data, confident = 8) %>%
  filter(!is.na(confident)) %>%
  unnest_tokens(output = "word", input = "confident") %>%
  count(word) %>%
  filter(!word %in% omitted) %>%
  slice_max(order_by = n, n = 25, with_ties = FALSE)

ggplot(words, aes(label = word, colour = word, size = n)) +
  geom_text_wordcloud_area() +
  scale_size_area(max_size = 20) +
  theme_minimal(base_size = 14) +
  scale_color_see_d(palette = "ice") 
```

Row {data-height=600}
-----------------------------------------------------------------------

### Confident 

```{r}
select(data, confident = 7) %>%
  filter(!is.na(confident)) %>%
  kable(row.names = FALSE, col.names = "") %>%
  kable_classic(lightable_options = "striped")
```


### Not Confident 

```{r}
select(data, confident = 8) %>%
  filter(!is.na(confident)) %>%
  kable(row.names = FALSE, col.names = "") %>%
  kable_classic(lightable_options = "striped")
```
