---
title: 'Formative Exercise 04: Data'
output: 
  html_document:
    df_print: kable
---

```{r setup, include=FALSE}
# please do not alter this code chunk
knitr::opts_chunk$set(echo = TRUE,
                      message = TRUE, 
                      error = TRUE)

library(tidyverse)
library(reprores)
library(readxl)

# install the class package reprores to access built-in data
# devtools::install_github("psyteachr/reprores-v2)
# or download data from the website
# https://psyteachr.github.io/reprores/data/data.zip
```

## Load built-in datasets

List the datasets in `dplyr`.

```{r Q1}
data(package = "dplyr")
```


Load the built-in dataset `starwars` and use `glimpse()` to see an overview.

```{r Q2}
data(starwars)

glimpse(starwars)
```


Convert the built-in base R `mtcars` dataset to a tibble (you will need to find the function for this; it isn't in the chapter), and store it in the object `mt`.

```{r Q3}
mt <- as_tibble(mtcars)
```


## Import data from CSV and Excel files

Using the data directory created by `reprores::getdata()` (or download [the zip file](https://psyteachr.github.io/reprores/data/data.zip), read "disgust_scores.csv" into a table.

```{r Q4}
disgust <- read_csv("data/disgust_scores.csv")
```

Override the default column specifications to skip the `id` column.

```{r Q5}
disgust_skip <- read_csv("data/disgust_scores.csv", 
                         col_select = -1)
```


How many rows and columns are in the `disgust` dataset?

```{r Q6}
disgust_rows <- nrow(disgust)
disgust_cols <- ncol(disgust)
```


Load the data in "data/stroop.csv" as `stroop1` and "data/stroop.xlsx" as `stroop2`.

```{r Q7}
stroop1 <- read_csv("data/stroop.csv")
stroop2 <- readxl::read_excel("data/stroop.xlsx")
```

Use `glimpse()` to figure out the difference between the two data tables and fix the problem.

```{r Q8}
glimpse(stroop1)
glimpse(stroop2)
stroop2b <- readxl::read_excel(
  path = "data/stroop.xlsx",
  na = c("", "NA", "missing", 999)
)

glimpse(stroop2b)
```


## Create a data table

Create a tibble with the columns `name`, `age`, and `country` of origin for 2 people you know.

```{r Q9}
people <- tibble(
  name = c("Robbie", "Kris"),
  age = c(14, 31),
  country = c("Scotland", "Philippines")
)

people
```

Create a tibble that has the structure of the table below, using the minimum typing possible. (Hint: `rep()`).  Store it in the variable `my_tbl`.

ID |  A | B   | C
--|-----|-----|---
1	| A1	| B1	| C1	
2	| A1	| B2	| C1	
3	| A1	| B1	| C1	
4	| A1	| B2	| C1	
5	| A2	| B1	| C1	
6	| A2	| B2	| C1	
7	| A2	| B1	| C1	
8	| A2	| B2	| C1

```{r Q10}
my_tbl <- tibble(
  ID = 1:8,
  A = rep(c("A1", "A2"), each = 4),
  B = rep(c("B1", "B2"), 4),
  C = "C1"
) 

my_tbl
```

## Understand the use the basic data types

Set the following objects to the number 1 with the indicated data type:

* `one_int` (integer)
* `one_dbl` (double)
* `one_chr` (character)

```{r Q11}
one_int <- 1L
one_dbl <- 1.0
one_chr <- "1"
```

Set the objects `T_log`, `T_chr`, `T_int` and `T_dbl` to logical, character, integer and double values that will all be equal to `TRUE`. 

```{r Q12}
T_log <- TRUE
T_chr <- "TRUE"
T_int <- 1L
T_dbl <- 1.0
```

Check your answers with this code:

```{r Q12-check}
# these should all evaluate to TRUE
tests <- list(
  T_log_is_TRUE = T_log == TRUE,
  T_chr_is_TRUE = T_chr == TRUE,
  T_int_is_TRUE = T_int == TRUE,
  T_dbl_is_TRUE = T_dbl == TRUE,
  T_log_is_log = is.logical(T_log),
  T_chr_is_chr = is.character(T_chr),
  T_int_is_int = is.integer(T_int),
  T_dbl_is_dbl = is.double(T_dbl)
)

str(tests) # this shows a condensed version of the list
```


## Understand and use the basic container types

Create a vector of the numbers 3, 6, and 9.

```{r Q13}
threes <- c(3, 6, 9)
```


The built-in vector `letters` contains the letters of the English alphabet.  Use an indexing vector of integers to extract the letters that spell 'cat'.

```{r Q14}
cat <- letters[c(3, 1, 20)]

select <- rep(c(T, F), each = 13)
letters[select]


subject_ids <- 100:140

select <- rep(c(T, F), each = 2, 
              length.out = length(subject_ids))
subject_ids[select]
```


The function `colors()` returns all of the color names that R is aware of. What is the length of the vector returned by this function? (Use code to find the answer.)

```{r Q15}
col_length <- length(colors())
```


Create a named list called `col_types` where the name is each column in the built-in dataset `table1` and the value is the column data type (e.g., "double", "character", "integer", "logical").

```{r Q16}
table1
col_types <- list(
  country = "character", 
  year = "integer",
  cases = "integer",
  population = "integer"
)
```


## Use vectorized operations

Set the object `x` to the integers 1 to 100. Use vectorised operations to set `y` to `x` squared. Use `plot(x, y)` to visualise the relationship between these two numbers.

```{r Q17}
x <- 1:100
y <- x^2

plot(x, y)
```

Set `t` to the numbers 0 to 100 in increments of 0.1. Set `x` to the sine of `t` and `y` to the cosine of `t` (you will need to find the functions for sine and cosine). Plot `x` against `y`.

```{r Q18}
t <- seq(from = 0, to = 100, by = .1)
x <- sin(t)
y <- cos(t)

plot(x, y)
```


The function call `runif(n, min, max)` will draw `n` numbers from a uniform distribution from `min` to `max`. If you set `n` to 10000, `min` to 0 and `max` to 1, this simulates the p-values that you would get from 10000 experiments where the null hypothesis is true. Create the following objects:

* `pvals`: 10000 simulated p-values using `runif()`
* `is_sig`: a logical vector that is `TRUE` if the corresponding element of `pvals` is less than .05, `FALSE` otherwise
* `sig_vals`: a vector of just the significant p-values
* `prop_sig`: the proportion of those p-values that were significant

```{r Q19}
set.seed(92319) # ensures you get the same random numbers each time you run this code chunk

pvals    <- runif(n = 10000, min = 0, max = 1)
is_sig   <- pvals < .05
sig_vals <- pvals[is_sig]
prop_sig <- mean(is_sig)
```


```{r}
ct <- "ccccd"

# value "missing" in rt column
stroop <- read_csv("data/stroop.csv", col_types = ct)

glimpse(stroop)
```


