---
title: 'Formative Exercise 08: GLM'
output: 
  html_document:
    df_print: kable
---

```{r setup, include=FALSE}
# please do not alter this code chunk
knitr::opts_chunk$set(echo = TRUE,
                      message = TRUE, 
                      error = TRUE)

library(broom)
library(tidyverse)
library(reprores)

# install the class package reprores to access built-in data
# devtools::install_github("psyteachr/reprores-v2)
# or download data from the website
# https://psyteachr.github.io/reprores/data/data.zip
```

## The `personality_scores` dataset

Load the dataset [reprores::personality_scores](https://psyteachr.github.io/reprores/data/personality_scores.csv).

```{r data}
personality_scores <- reprores::personality_scores
```


### Question 1

Use ggplot2 to visualise the relationship between extraversion (`Ex`) on the horizontal axis and neuroticism (`Ne`) on the vertical axis. 

```{r Q1}
ggplot(data = personality_scores,
       mapping = aes(x = Ex, y = Ne)) +
  geom_point(alpha = 0.05, na.rm = TRUE) +
  geom_smooth(method = lm, formula = y ~ x, na.rm = TRUE)
```


### Question 2

Run a regression model that predicts neuroticism from extraversion, and store the model object in the variable `personality_mod`.  End the block by printing out the summary of the model.

```{r Q2}
personality_mod <- lm(formula = Ne ~ Ex, 
                      data = personality_scores)

summary(personality_mod)
```



### Question 3

Make a histogram of the residuals of the model using ggplot2.

```{r Q3}
residuals <- resid(personality_mod)
residuals <- personality_mod$residuals
hist(residuals)
```


```{r}
int <- personality_mod$coefficients[["(Intercept)"]]
Ex_coef <- personality_mod$coefficients[["Ex"]]

slice(personality_scores, 1:10) %>%
  select(Ne, Ex) %>%
  mutate(predictedNe = int + (Ex * Ex_coef)) %>%
  mutate(residual = Ne - predictedNe) %>%
  mutate(resid = residuals)
```


### Question 4

Write code to predict the neuroticism score for the minimum, mean, and maximum  extraversion scores.  Store the vector of predictions in the variable `personality_pred`.

```{r Q4}
int <- personality_mod$coefficients[["(Intercept)"]]
Ex_coef <- personality_mod$coefficients[["Ex"]]

personality_pred <- personality_scores %>%
  summarise(min = min(Ex, na.rm = TRUE),
            mean = mean(Ex, na.rm = TRUE),
            max = max(Ex, na.rm = TRUE)
            ) %>%
  pivot_longer(cols = min:max,
               names_to = "type",
               values_to = "Ex") %>%
  mutate(Ne = int + (Ex * Ex_coef)) %>%
  print()
```


## Simulating data from the linear model

### Question 5

*NOTE: You can knit this file to html to see formatted versions of the equations below (which are enclosed in `$` characters); alternatively, if you find it easier, you can hover your mouse pointer over the `$` in the code equations to see the formatted versions.* 

Write code to randomly generate 10 Y values from a simple linear regression model with an intercept of 3 and a slope of -7.  Recall the form of the linear model:

$Y_i = \beta_0 + \beta_1 X_i + e_i$

The residuals ($e_i$s) are drawn from a normal distribution with mean 0 and variance $\sigma^2 = 4$, and $X$ is the vector of integer values from 1 to 10. Store the 10 observations in the variable `Yi` below. (NOTE: the standard deviation is the *square root* of the variance, i.e. $\sigma$; `rnorm()` takes the standard deviation, not the variance, as its third argument).

```{r Q5}
X <- 1:10
err <- rnorm(n = 10, mean = 0, sd = sqrt(4))
Yi <- 3 + (X * -7) + err


plot(X, Yi)
```

```{r}
set.seed(90210)
simdat <- faux::sim_design(
  between = list(
    condition = c("A", "B")
  ),
  n = c(A = 20, B = 30),
  mu = c(100, 105),
  sd = c(10, 11),
  dv = "score"
)
```

```{r}
simdat <- simdat %>%
  mutate(condition.t = recode(condition, A = 0, B = 1)) %>%
  mutate(condition.e = recode(condition, A = -.5, B = .5)) %>%
  mutate(condition.e2 = recode(condition, A = .5, B = -.5)) %>%
  mutate(condition.s = recode(condition, A = -1, B = 1)) %>%
  print()
```



```{r}
mod <- lm(formula = score ~ condition,
          data = simdat)

summary(mod)$coefficients
```

## Treatment-coded
```{r}
mod <- lm(formula = score ~ condition.t,
          data = simdat)

summary(mod)$coefficients
```
## Effect-coded
```{r}
mod <- lm(formula = score ~ condition.e,
          data = simdat)

summary(mod)$coefficients
```

```{r}
int <- mod$coefficients[["(Intercept)"]]
cond_coef <- 0.5
err_sd <- sigma(mod)
n <- 50

newdat <- tibble(
  id = 1:n,
  condition = rep(c("A", "B"), each = n/2)
) %>%
  mutate(condition.e = recode(condition, A = -.5, B = .5)) %>%
  mutate(
    err = rnorm(n = nrow(.), mean = 0, sd = err_sd),
    score = int + (condition.e * cond_coef) + err
  )


mod <- lm(score ~ condition.e, data = newdat)

broom::tidy(mod)
```



## Reverse Effect-coded
```{r}
mod <- lm(formula = score ~ condition.e2,
          data = simdat)

summary(mod)$coefficients
```

## Sum-coded
```{r}
mod <- lm(formula = score ~ condition.s,
          data = simdat)

summary(mod)$coefficients
```
