---
title: 'Formative Exercise 09: Functions'
output: 
  html_document:
    df_print: kable
---

```{r setup, include=FALSE}
# please do not alter this code chunk
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE, 
                      error = TRUE)

library(tidyverse)
library(broom)
```

Edit the code chunks below and knit the document. You can pipe your objects to `glimpse()` or `print()` to display them.

## Basic Iteration Functions

### Question 1

Set the vector `v1` equal to the following: 11, 13, 15, 17, 19, ..., 99, 101 (use a function; don't just type all the numbers).

```{r Q1}
v1 <- seq(from = 11, to = 99, by = 2) %>% print()
```

### Question 2

Set the vector `v2` equal to the following: "A" "A" "B" "B" "C" "C" "D" "D" "E" "E" (note the letters are all uppercase).

```{r Q2}
v2 <- rep(LETTERS[1:5], each = 2) %>% print()
```

### Question 3

Set the vector `v3` equal to the words "dog" 10 times, "cat" 9 times, "fish" 6 times, and "ferret" 1 time. 

```{r Q3}
v3 <-  rep(c("dog", "cat", "fish", "ferret"), 
           times = c(10, 9, 6, 1)) %>%
  print()
```

## map and apply functions

### Question 4a

Use `apply()` or `map()` functions to create a list of 11 vectors of 100 numbers sampled from 11 random normal distributions with means of 0 to 1.0 (in steps of 0.1) and SDs of 1. Assign this list to the object `samples`. Set the seed to `321` before you generate the random numbers to ensure reproducibility.


```{r Q4a}
means <- seq(0, 1, .1)
samples <- map(.x = means, 
               .f = rnorm, n = 100, sd = 1)
```

don't use map for this...

```{r}
iris %>%
  pivot_longer(cols = Sepal.Length:Petal.Width,
               names_to = "variable",
               values_to = "value") %>%
  group_by(variable) %>%
  summarise(mean = mean(value),
            sd = sd(value))
```


### Question 4b

Use `apply()` or `map()` functions to create a vector of the sample means from the list `samples` in the previous question.

```{r Q4b}
x <- samples[[1]]
mean(x)

sample_means <- map_dbl(samples, .f = mean) %>%
  print()
```

## Custom functions

### Question 5a

Write a function called `my_add` that adds two numbers (`x` and `y`) together and returns the results.

```{r Q5a}
my_add <- function(x, y) {
  x + y
}

my_add(x = 3, y = 4)
my_add(x = 3, y = 5)
```

### Question 5b

Create a vector testing your function `my_add`. Every item in the vector should evaluate to `TRUE` if your function is working correctly.

```{r Q5b}
my_add_test <- c(
  my_add(0, 1) == 1,
  my_add(-1, -3) == -4,
  my_add(0.5, 0.3) == 0.8,
  my_add("1", "2") == 3
) %>%
  print()
```

## Error handling

### Question 6

Copy the function `my_add` above and add an error message that returns "x and y must be numbers" if `x` or `y` are not both numbers.

```{r Q6}
my_add <- function(x, y) {
  # check if x and y are numbers
  if (!is.numeric(x)) stop("x must be a number")
  
  if (!is.numeric(y)) stop("y must be a number")
  
  x + y
}


my_add("002", "4")
```

## Building up a custom function

### Question 7

Create a tibble called `dat` that contains 20 rows and three columns: `id` (integers 101 through 120), `pre` and `post` (both 20-item vectors of random numbers from a normal distribution with mean = 0 and sd = 1). Set seed to `90210` to ensure reproducible values.

```{r Q7}
dat <- tibble(
  id = 101:120,
  pre = rnorm(n = 20, mean = 0, sd = 1),
  post = rnorm(n = 20, mean = 0, sd = 1)
)

dat2 <- tibble(
  id = 1:30,
  group = rep(c("A", "B"), time = c(10, 20)),
  dv = c(rnorm(n = 10, mean = 0, sd = 1),
         rnorm(n = 20, mean = 0.5, sd = 1))
)
```

### Question 8

Run a two-tailed, *paired-samples* t-test comparing `pre` and `post`. (check the help for `t.test`)

```{r Q8}
t <- t.test(dat$pre, dat$post, paired = TRUE) %>% 
  print()
```

### Question 9

Use `broom::tidy` to save the results of the t-test in question 8 in a table called `stats`.

```{r Q9}
stats <- broom::tidy(t) %>%
  print()

stats$p.value
```

### Question 10

Create a function called `report_t` that takes a data table as an argument and returns the result of a two-tailed, paired-samples t-test between the columns `pre` and `post` in the following format: 

"The mean increase from pre-test to post-test was #.###: t(#) = #.###, p = 0.###, 95% CI = [#.###, #.###]." 

Hint: look at the function `paste0()` (simpler) or `sprintf()` (complicated but more powerful).

NB: Make sure all numbers are reported to three decimal places (except degrees of freedom).

```{r Q10}
report_t <- function(data) {
  t <- t.test(data$pre, data$post, paired = TRUE)
  stats <- broom::tidy(t)
  glue::glue("The mean increase from pre-test to post-test was {inc}: t({df}) = {t}, p = {p}, 95% CI = [{ci1}, {ci2}].",
             inc = round(stats$estimate, 2),
             df = round(stats$parameter),
             t = round(stats$statistic, 3),
             p = round(stats$p.value, 3),
             ci1 = round(stats$conf.low, 3),
             ci2 = round(stats$conf.high, 3)
             )
}

report_t(dat)
```


### Question 11

Use inline R to include the results of `report_t()` on the `dat` data table in a paragraph below.

`r report_t(dat)`


## Functions and GLM

### Question 12

Write a function to simulate data with the form.

$Y_i = \beta_0 + \beta_1 X_i + e_i$

The function should take arguments for the number of observations to return (`n`), the intercept (`b0`), the effect (`b1`), the mean and SD of the predictor variable X (`X_mu` and `X_sd`), and the SD of the residual error (`err_sd`). The function should return a tibble with `n` rows and the columns `id`, `X` and `Y`.

```{r Q12}

sim_lm_data <- function(n, # number of observations
                        b0 = 0, # intercept
                        b1 = 0,
                        X_mu = 0, 
                        X_sd = 1,
                        err_sd = 1) {
  # add code here and define arguments above
  
  X <- rnorm(n = n, mean = X_mu, sd = X_sd)
  error <- rnorm(n = n, mean = 0, sd = err_sd)
  Y <- b0 + (b1 * X) + error
  
  tibble(
    id = 1:n,
    X = X,
    Y = Y
  )
}

dat12 <- sim_lm_data(n = 10, b0 = 100, b1 = 0.5, err_sd = 10) %>% print() # do not edit

plot(dat12$X, dat12$Y)
```

### Question 13

Use the function from Question 12 to generate a data table with 10000 subjects, an intercept of 80, an effect of X of 0.5, where X has a mean of 0 and SD of 1, and residual error SD of 2.

```{r Q13a}
dat13 <- sim_lm_data(n = 10000, 
                     b0 = 80, 
                     b1 = 0.5, 
                     err_sd = 2)
```

Analyse the data with `lm()`. Find where the analysis summary estimates the values of `b0` and `b1`. What happens if you change the simulation values?

```{r Q13b}
mod13 <- lm(Y ~ X, data = dat13)
```


### Question 14

Use the function from Question 6 to calculate power by simulation for the effect of X on Y in a design with 50 subjects, an intercept of 80, an effect of X of 0.5, where X has a mean of 0 and SD of 1, residual error SD of 2, and alpha of 0.05.

Hint: use `broom::tidy()` to get the p-value for the effect of X.

```{r Q14}

n = 50

pilot_b1 <- 1.2

powsim <- function(n, b1) {
  simdata <- sim_lm_data(n = n, 
                     b0 = 80, 
                     b1 = b1, 
                     err_sd = 2)
  mod <- lm(Y ~ X, data = simdata)
  
  stats <- broom::tidy(mod)
  
  stats$p.value[[2]]
}

p <- replicate(n = 1000, expr = powsim(n = 50, b1 = 0.5))
hist(p)
mean(p < 0.05)
```

### Question 15

Calculate power (i.e., the false positive rate) for the effect of X on Y in a design with 50 subjects where there is no effect and alpha is 0.05.

```{r Q15}
p <- replicate(1000, powsim(n = 50, b1 = 0))
false_pos <- mean(p < .025) %>% print()

hist(p)
```

Make a histogram of the p-values from the simulation above. Use geom_histogram with `binwidth=0.05` and `boundary=0`. What kind of distribution is this?

```{r Q15b}
ggplot(mapping = aes(x = p)) +
  geom_histogram(boundary = 0, binwidth = 0.05)
```

