---
title: "Extra Help"
author: "Lisa DeBruine"
date: "07/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Joining Datasets

### Row binding

add together data with the same structure

```{r}
a1 <- tibble(
  id = 1:10,
  dv = rnorm(10)
) %>%
  mutate(condition = "A")

a2 <- tibble(
  id = 11:20,
  dv = rnorm(10)
) %>%
  mutate(condition = "B")
```

```{r}
a <- bind_rows(a1, a2)
```

### joining

```{r}
b <- tibble(
  id = sample(0:19),
  version = sample(c("x", "y"), 20, TRUE)
)
```

```{r}
x <- inner_join(a, b, by = "id")
```

## Which functions which library

```{r}
?pivot_wider
```

## time-consuming functions

- run functions in an external script or in an unevaluated code chunk and save results to CSV or RData

```{r, eval = FALSE}
# long code
simfunc <- function(n) {

}

analysis <- function(data) {

}


p <- replicate(100, analysis())

results_table <- tibble(
  n = seq(100, 1000, by = 100),
  power = seq(.2, .9, length.out = 10)
)

save(results_table, file = "results_table.RData")
# save as RData
```

Then load

```{r}
# load data created by script.R
load("results_table.RData")
```

## Demographic summary tables with NAs

```{r}
demog <- tibble(
  id = 1:5,
  age = c(20, 20, 21, NA, 19)
)

summarise(demog, n = n(), 
          missing_age = sum(is.na(age)),
          has_age = sum(!is.na(age)),
          age = mean(age, na.rm = TRUE))
```

## power.t.test for checking

```{r}
power.t.test(
  #n = 500, # n from your simulation
  delta = 1.5, # difference between groups
  sd = 5.3, # calculate from pilot data
  sig.level = 0.01, # alpha
  type = "two.sample",
  power = 0.9
)
```

## Slow computer

Use smaller number of iterations to narrow down the range of n to search over.

Use https://rstudio.psy.gla.ac.uk if your laptop is very slow.

```{r}
power.t.test(
  n = 370, # n from your simulation
  delta = 1.5, # difference between groups
  sd = 5.3, # calculate from pilot data
  sig.level = 0.01, # alpha
  type = "two.sample"
)
```


```{r}
m <- lm(mpg ~ vs, mtcars)

summary(m)
```

get values for reporting from broom::tidy.

```{r}
vs <- broom::tidy(m, conf.int = TRUE) %>%
  filter(term == "vs")

vs_est <- sprintf("%.2f", vs$estimate)
vs_se <- sprintf("%.2f", vs$std.error)
vs_ci <- sprintf("95%% CI = [%.2f, %.2f]", 
                 vs$conf.low,
                 vs$conf.high)
vs_t <- sprintf("t = %.2f", vs$statistic)

if (vs$p.value < .001) {
  vs_p <- "p < .001"
} else {
  vs_p <- sprintf("p = %.3f", vs$p.value)
}
```


The main effect of vs had an estimate of `r vs_est` (`r vs_ci`), which was significant (`r vs_t`, `r vs_p`). This indicates that group 1 had, on average, `r vs_est` mpg higher mileage per gallon than group 0.


The main effect of vs was significant (t = `r vs_t`, `r vs_p`), such that group 1 had, on average, `r vs_est` mpg (SE = `r vs_se`) higher mileage per gallon than group 0.


## How do you know what direction the group effects are in?

```{r}
mtcars %>%
  group_by(vs) %>%
  summarise(m = mean(mpg))
```

```{r}
x <- tibble(id = 1:10)
save(x, file = "table.RData")
load("table.RData")

table <- "table.RData"
```

