---
title: "Reproducible Report Demo"
author: "Lisa DeBruine"
bibliography: biblio.bib
output: 
  bookdown::html_document2:
    toc: true
    toc_float: true
    number_sections: false
    df_print: kable
    theme: 
      version: 4
      bootswatch: journal
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = TRUE,
                      message = TRUE)

library(tidyverse)
library(kableExtra)

theme_set(theme_bw())
```


```{r}
# load questionnaire data

data_quest_raw <- read_csv("data/questions.csv", 
                           show_col_types = FALSE)

## reverse-code questions

# straighforward but tedious
data_quest_rev <- data_quest_raw %>%
  mutate(q02R = 8 - q02R,
         q04R = 8 - q04R,
         q06R = 8 - q06R,
         q08R = 8 - q08R,
         q10R = 8 - q10R,
         q12R = 8 - q12R,
         q14R = 8 - q14R)

# fancier but more extendable
data_quest_rev <- data_quest_raw %>%
  pivot_longer(cols = -(subj_id)) %>%
  separate(col = name, into = c("q", "rev"), sep = -1) %>%
  mutate(rev_score = ifelse(rev == "R", 8 - value, value))
  
  
## create summary disgust score
data_quest_summary <- data_quest_rev %>%
  group_by(subj_id) %>%
  summarise(score = sum(rev_score))

```


```{r}
## load subject data

subj_A1 <- read_csv("data/subjects_condition-A_version-1.csv",
                    na = c("NA", "missing"), show_col_types = FALSE) %>%
  mutate(condition = "A", version = "One")
subj_A2 <- read_csv("data/subjects_condition-A_version-2.csv",
                    na = c("NA", "missing"), show_col_types = FALSE) %>%
  mutate(condition = "A", version = "Two")
subj_B1 <- read_csv("data/subjects_condition-B_version-1.csv",
                    na = c("NA", "missing"), show_col_types = FALSE ) %>%
  mutate(condition = "B", version = "One")
subj_B2 <- read_csv("data/subjects_condition-B_version-2.csv",
                    na = c("NA", "missing"), show_col_types = FALSE) %>%
  mutate(condition = "B", version = "Two")

## join subject data

data_subj <- bind_rows(subj_A1, subj_A2, subj_B1, subj_B2)
```

```{r}
# join all data
data_all <- full_join(data_subj, data_quest_summary, by = "subj_id")

# exclude subjects with missing language, score, or condition
data_analysis <- data_all %>%
  filter(language == "monolingual", 
         !is.na(score), 
         !is.na(condition)) %>%
  mutate(condition.e = recode(condition, A = -0.5, B = 0.5))
```

```{r}
total_n <- nrow(data_all)
included_n <- nrow(data_analysis)
excluded_n <- total_n - included_n
```



## Intro

The study asked `r total_n` subjects to complete a 15-item disgust scale and report their age, gender, and whether they were monolingual or bilingual. Subjects were in one of two conditions (A or B) and one of two versions (One or Two). 

The script uses the following packages: tidyverse [@tidyverse].

## Demographics

### Full Data Set

See Table \@ref(tab:demog-all).

```{r demog-all}
# table of N per condition/version/language
data_all %>%
  count(condition, version, language) %>%
  pivot_wider(names_from = language, 
              values_from = n) %>%
  mutate(total = bilingual + monolingual) %>%
  kable(caption = "The number of bilingual and monolingial subjects per conditon and version in the full data set (pre-exclusions).") %>%
  kable_minimal()
```


#### Age 

Figure \@ref(fig:age-plot) shows that the age distributions were roughly similar between conditions, versions, and languages.

```{r age-plot, fig.cap="Age distributions by language, condition, and version", warning=FALSE}
ggplot(data_all, aes(x = age, color = language)) +
  geom_freqpoly(binwidth = 1) +
  facet_grid(version~condition, labeller = label_both)
```

#### Gender

```{r}
gender <- data_all %>% count(gender)
```


There were no obvious differences in the gender distribution between languages, conditions, and versions. However, there were more men (`r gender$n[[2]]`) than women (`r gender$n[[1]]`), non-binary people (`r gender$n[[3]]`), and people who did not answer the gender question (`r gender$n[[4]]`).

```{r gender-plot, fig.cap="Gender by language, condition, and version"}
ggplot(data_all, aes(x = gender, fill = language)) +
  geom_bar(position = "dodge") +
  facet_grid(version~condition, labeller = label_both)
```


### Exclusions

Because we were only looking at the effect of condition on disgust score for monolingual subjects, we excluded `r excluded_n` subjects who were bilingual or had missing disgust scores, leaving `r included_n` subjects for the analysis. 

```{r demog-subset}
# table of N per condition/version/language
data_analysis %>%
  count(condition, version) %>%
  kable(caption = "The number of subjects per conditon and version in the analysed data set (post-exclusions).") %>%
  kable_minimal()
```


#### Age 

Figure \@ref(fig:age-subplot) shows that the age distributions were roughly similar between conditions and versions.

```{r age-subplot, fig.cap="Age distributions by language, condition, and version", warning=FALSE}
ggplot(data_analysis, aes(x = age)) +
  geom_freqpoly(binwidth = 1, color = "#01BFC4") +
  facet_grid(version~condition, labeller = label_both)
```

#### Gender

```{r}
sub_gender <- data_analysis %>% count(gender)
```


The gender distribution between conditions and versions showed that there were more women in cndition B than condition A. There were more men (`r sub_gender$n[[2]]`) than women (`r sub_gender$n[[1]]`), non-binary people (`r sub_gender$n[[3]]`), and people who did not answer the gender question (`r sub_gender$n[[4]]`).

```{r gender-subplot, fig.cap="Gender by language, condition, and version"}
ggplot(data_analysis, aes(x = gender)) +
  geom_bar(fill = "#01BFC4") +
  facet_grid(version~condition, labeller = label_both)
```

## Analysis


```{r analysis-viz, fig.cap = "Disgust scores by condition for the monolingual subjects. The dot is the mean and error bars represent the 95% CI."}
ggplot(data_analysis, aes(x = condition, y = score)) +
  geom_violin() +
  stat_summary(fun.data = "mean_cl_boot") +
  ylab("Disgust Score")
```

Condition was effect-coded such that condition A = -0.5 and condition B = 0.5.

```{r lm}
model <- lm(score ~ condition.e, data = data_analysis)
stats <- broom::tidy(model, conf.int = TRUE, conf.level = 0.95)

t_val <- stats$statistic[[2]] %>% round(2)
p_val <- stats$p.value[[2]] %>% round(2)
condition_effect <- stats$estimate[[2]] %>% round(2)

stats %>%
  mutate(CI = sprintf("[%.2f -- %.2f]", conf.low, conf.high)) %>%
  select(-conf.low, -conf.high) %>%
  kable(digits = 2,
        col.names = c("Term", "Estimate", "SE", "t-value", "p-value", "95% CI"),
        caption = "Results of the linear model predicting disgust score from condition.") %>%
  kable_minimal()

```

The analysis showed that, although disgust scores in condition B were on average `r condition_effect` points larger than in condition B, the conditions were not significantly different (t = `r t_val`, p = `r p_val`).

## Power

Here I determined the sample size needed to have 85% power to detect a 0.5-point difference between the levels of condition with an alpha criterion of 0.01.

Here, we assume an equal number of people in conditions A and B. 

```{r}
# define constants
target_power <- .85
target_effect <- 0.5
target_alpha <- 0.01
sigma <- sigma(model)
model_int <- stats$estimate[[1]]

# power function
powersim <- function(n_per_condition) {
  ## simulate data with these parameters
  data_sim <- tibble(
    subj_id = 1:(n_per_condition*2),
    condition = rep(c("A", "B"), each = n_per_condition)
  ) %>%
    mutate(condition.e = recode(condition, A = -0.5, B = 0.5),
           error = rnorm(2*n_per_condition, mean = 0, sd = sigma),
           score = model_int + (condition.e * target_effect) + error
           )
  
  sim_model <- lm(score ~ condition.e, data = data_sim)
  sim_stats <- broom::tidy(sim_model)
  p <- sim_stats$p.value[[2]]
  
  return(p)
}
```


```{r}
# power analysis
set.seed(8675309)
n <- 16000
sim_p <- replicate(500, powersim(n))
power <- mean(sim_p < target_alpha)
```

Power analysis by simulation showed that you need approximately `r n` subjects per condition for a power of `r power*100`%.

## References


